---
output:
  html_document:
    highlight: null
    css: style.css
    self_contained: no
    keep_md: true
---

```{r, echo=FALSE}
library(stringr)

date <- "10/5/2017"
vendor <- "Pizza Capri"
title <- "Information, Spatial Selection, and the Statistics of Neighborhoods"
file_title <- "Statistics of Neighborhoods"
short_title_n = 3
speaker <- "Luís Bettencourt"
department <- "Mansueto Institute for Urban Innovation"
university <- "University of Chicago"
github_home <- "https://github.com/uchicago-computation-workshop"


```

```{r, echo=FALSE}
#Function to Shorten Title
small_title <- function(x, n=3) {
  ul <- unlist(strsplit(x, split = "\\s+"))[1:n]
  paste(ul,collapse=" ")
}

#Characters
unwanted_array = list(    'Š'='S', 'š'='s', 'Ž'='Z', 'ž'='z', 'À'='A', 'Á'='A', 'Â'='A', 'Ã'='A', 'Ä'='A', 'Å'='A', 'Æ'='A', 'Ç'='C', 'È'='E', 'É'='E',
                            'Ê'='E', 'Ë'='E', 'Ì'='I', 'Í'='I', 'Î'='I', 'Ï'='I', 'Ñ'='N', 'Ò'='O', 'Ó'='O', 'Ô'='O', 'Õ'='O', 'Ö'='O', 'Ø'='O', 'Ù'='U',
                            'Ú'='U', 'Û'='U', 'Ü'='U', 'Ý'='Y', 'Þ'='B', 'ß'='Ss', 'à'='a', 'á'='a', 'â'='a', 'ã'='a', 'ä'='a', 'å'='a', 'æ'='a', 'ç'='c',
                            'è'='e', 'é'='e', 'ê'='e', 'ë'='e', 'ì'='i', 'í'='i', 'î'='i', 'ï'='i', 'ð'='o', 'ñ'='n', 'ò'='o', 'ó'='o', 'ô'='o', 'õ'='o',
                            'ö'='o', 'ø'='o', 'ù'='u', 'ú'='u', 'û'='u', 'ý'='y', 'ý'='y', 'þ'='b', 'ÿ'='y' )


#Year
year <- substr(date, nchar(date)-4+1, nchar(date))

#Author Name
author_clean_lower <- str_replace_all(str_to_lower(speaker), " ", "_")

#Remove Unwanted Characters
out <- author_clean_lower
for(i in seq_along(unwanted_array))
    out <- gsub(names(unwanted_array)[i],unwanted_array[i],out)
author_clean <- out
author_lastname <- tail(strsplit(author_clean,split="_")[[1]],1)

#Repository Name
#repo = paste(year, author_clean, sep = "_")
repo = author_clean
issues_page <- paste(github_home, repo, "issues", sep="/")
repo_page <- paste(github_home, repo, sep="/")

#Create File Name Parts
short_title <- small_title(file_title, short_title_n)
paper_file <- paste(year, author_lastname, short_title, sep="  ")

#Clean Up File Name
punct <- '[]\\?!\"\'#$%&(){}+*/:;,._`|~\\[<=>@\\^-]'

#Remove Punctuation
lowered_name <- str_to_lower(paper_file)
stripped_name <- str_replace_all(lowered_name, punct, "")
cleaned_name <- str_replace_all(stripped_name, " ", "_")
cleaned_paper_file <- paste(cleaned_name, "pdf", sep=".")

#File Name Link
paper_link = paste(github_home, repo, "blob/master", cleaned_paper_file, sep="/"  )


#Clean Short Title
short_title_clean <- str_replace_all(short_title, punct, "")

```

<br>

<h3 class=pfblock-header> The Computation Workshop Presents </h3>

<h1 class=pfblock-header3> `r speaker` </h1>
<h3 class=pfblock-header3> `r department` </h3>
<h3 class=pfblock-header3> `r university` </h3>

<br><br>



<p class=pfblock-header3>The <a href="https://macss.uchicago.edu/content/computation-workshop"> Computation Workshop </a> at the University of Chicago cordially invites you to attend this week's talk:</p>

<br>

<div class=pfblock-header3>
<h2 class=pfblock-header> 
  <a href="`r paper_link`" >`r title`</a>
</h2>

<br>
</div>

<h4 class=pfblock-header3> Thursday, `r date` </h4>
<h4 class=pfblock-header3> 11:00am-12:20pm </h4>
<h4 class=pfblock-header3> Saieh Hall 247 </h4>

<br>

<p class=pfblock-header3>A light lunch will be provided by `r vendor`.</p>

<br><br>

<!--Insert Faculty Bio Here-->



<p class=footertext2> 

  **Luís M. A. Bettencourt** is the Pritzker Director of the Mansueto Institute for Urban Innovation at the University of Chicago. He is also a Professor of Ecology and Evolution at the University of Chicago and External Professor of Complex Systems at the Santa Fe Institute. 
    
  He was trained as a theoretical physicist and obtained his Licenciatura from Instituto Superior Técnico (Lisbon, Portugal) in 1992, and his PhD from Imperial College (University of London, UK) in 1996 for research in statistical and high-energy physics models of the early Universe.  He has held postdoctoral positions at the University of Heidelberg (Germany), Los Alamos National Laboratory (Director’s Fellow and Slansky Fellow) and at MIT (Center for Theoretical Physics).
    
  He has worked extensively on complex systems theory and on cities and urbanization, in particular. His research emphasizes the creation of new interdisciplinary synthesis to describe cities in quantitative and predictive ways, informed by classical theory from various disciplines and the growing availability of empirical data worldwide. 
    
  He is the author of over 100 scientific papers and several edited books. His research has been featured in leading media venues, such as the New York Times, Nature, Wired, New Scientist, and the Smithsonian.

</p>


<br><br>

---

<p class=footertext> The 2017-2018 <a href="https://macss.uchicago.edu/content/computation-workshop"> Computation Workshop </a> meets each Thursday from 11 to 12:20 p.m. in Saieh 247. All interested faculty and graduate students are welcome.</p> 

<p class=footertext>Students in the Masters of Computational Social Science program are expected to attend and join the discussion by posting a comment on the <a href="`r issues_page`"> issues page </a> of the <a href="`r repo_page`"> workshop's public repository on GitHub.</a></p>

<p class=footertext>This week, Luís was kind enough to contribute two papers, one in development and a related publication in PNAS. MACSS students should focus their response on the project in development: <a href="`r paper_link`" >`r title`</a>, since these comments will have a greater potential impact. Both papers are available <a href="`r repo_page`"> on Github for review. </a></p>

